From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics

### 2023-11-30 paper.qmd
Update manuscript plots for varying treatment effects

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction"))
```

@@

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip()
```

@@

```{R}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

@@

```{R}
#| fig-height: 7
summary.df <- lapply(fits, function(fit) {
    post <- post_summarise(fit, "delta", rename = T, model_info = T,
                           probs = c(0.025, 0.17, 0.5, 0.83, 0.975)) |>
        rename(median = `50%`,
               lower95 = `2.5%`,
               upper95 = `97.5%`,
               lower66 = `17%`,
               upper66 = `83%`)
}) |> bind_rows()

@@

```{R}
regtable <- function(fits, ...) {
    names(fits) <- NULL
    modelsummary(fits, pars = c("delta", "beta", "alpha"), statistic = "conf.int", ...)
}

@@

```{R}
m <- c("frozen-bin_5y-all", "strict_frozen-bin_5y-all",
       "frozen-bin_5y-high_intensity", "strict_frozen-bin_5y-high_intensity")
regtable(fits[m], title = "Binary Treatments - Last 5 Years")
```

```{R}
m <- c("frozen-prop-all", "strict_frozen-prop-all",
       "frozen-prop-high_intensity", "strict_frozen-prop-high_intensity")
regtable(fits[m], title = "Proportion Treatments")
```

>>>>

ll <- extract_digits(delta$variable)
delta$variable <- sprintf("delta[%s]", sapply(ll, `[`, 1))
delta$group <- sapply(ll, `[`, 2) |> as.factor()

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction")) +
    facet_grid(. ~ group)

@@

ll <- extract_digits(ame$variable)
ame$variable <- sprintf("ame[%s]", sapply(ll, `[`, 1))
ame$group <- sapply(ll, `[`, 2) |> as.factor()

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip() +
    facet_grid(. ~ group)
```

@@

```{R eval = F}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

@@

```{R eval = F}
#| fig-height: 7
summary.df <- lapply(fits, function(fit) {
    post <- post_summarise(fit, "delta", rename = T, model_info = T,
                           probs = c(0.025, 0.17, 0.5, 0.83, 0.975)) |>
        rename(median = `50%`,
               lower95 = `2.5%`,
               upper95 = `97.5%`,
               lower66 = `17%`,
               upper66 = `83%`)
}) |> bind_rows()

@@

```{R eval = F}
regtable <- function(fits, ...) {
    names(fits) <- NULL
    modelsummary(fits, pars = c("delta", "beta", "alpha"), statistic = "conf.int", ...)
}

@@

```{R eval = F}
m <- c("frozen-bin_5y-all", "strict_frozen-bin_5y-all",
       "frozen-bin_5y-high_intensity", "strict_frozen-bin_5y-high_intensity")
regtable(fits[m], title = "Binary Treatments - Last 5 Years")
```

```{R  eval = F}
m <- c("frozen-prop-all", "strict_frozen-prop-all",
       "frozen-prop-high_intensity", "strict_frozen-prop-high_intensity")
regtable(fits[m], title = "Proportion Treatments")
```
